Research Journal

### 2018-07-05 journal/main.tex

Figure \ref{fig:baseline_plot} shows an example of ground truth node embedding and similarities as well as the node embedding vectors and similarities of the initial embedding we use.

\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \subfloat[Sorted ground truth embedding and initial embedding]{
        \includegraphics[width=0.45\textwidth]{figures/baseline_embeddings.png}
        \label{fig:baseline_sub1}
    }
    \subfloat[Ground truth and initial similarity]{
        \includegraphics[width=0.45\textwidth]{figures/baseline_sim.png}
        \label{fig:baseline_sub2}
    }
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:baseline_plot}
\end{figure}

>>>>

% Figure \ref{fig:baseline_plot} shows an example of ground truth node embedding and similarities as well as the node embedding vectors and similarities of the initial embedding we use.
% 
\begin{figure}[H]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/noiseless_sim.png}
    \begin{minipage}{.45\linewidth}
        \subfloat[Sorted ground truth embedding and initial embedding]{ \includegraphics[width=0.9\textwidth]{figures/baseline_embeddings.png} \label{fig:baseline_sub1} }
    \end{minipage}
    \begin{minipage}{.45\linewidth}
        \subfloat[Ground truth and initial similarity]{ \includegraphics[width=0.9\textwidth]{figures/baseline_sim.png} \label{fig:baseline_sub2} }
    \end{minipage}
    \caption{Here we show a baseline for the node embedding vectors and the final similarity matrix}
    \label{fig:baseline_plot}
\end{figure}
